Peptide correlation analysis
============================

## The `PeCorA` package


`PeCorA` is a package that contains a number of functions to detect discordant peptide quantities in shotgun proteomics sata by Peptide Correlation Analysis. The package also contains a number of published proteomics datasets processed with different processing tools. 


### Installation
You can install `PeCorA` from github downloading the package by cloning the repository.

`$ git clone https://github.com/demar01/PeCorA.git`

`$ R CMD INSTALL PeCorA-master`

Once installed, load the package by writing in the console

```{r}
library(PeCorA)
```

### Available datasets

Currently, there are three datasets available in `PeCorA`.

Data                    |Description                                                                                                          |
|:-----------------------|:--------------------------------------------------------------------------------------------------------------------|
|PeCorA_noZ   |Primary mouse microglia dataset (PXD014466)|
|input.dda.iprg.pg  |BRF Proteome Informatics Research Group (iPRG) 2015 Study: Detection of Differentially Abundant Proteins in Label-Free Quantitative LC-MS/MS Experiments |
|Covid_peptides  |Large-scale proteomic Analysis of COVID-19 Severity|

### Loading data

Data is loaded into the `R` session using the `load` function; for
instance, to get the DDA iPRG data from
[Choi et al 2017](https://pubmed.ncbi.nlm.nih.gov/27990823/):

```{r}
data("input.dda.iprg.pg")
```

To get more information about a dataset, see its manual page

```{r}
?input.dda.iprg.pg
```

### Functions
The main function of the package is called `PeCorA`, which fits a linear model with interaction between peptides and biological treatment groups.


### Vignette 
See [Vignette](https://github.com/demar01/PeCorA/blob/master/vignettes/PeCorA_vignette.pdf) for complete workflow.


### Contact
If you have any questions or suggestions please contact us:

Maria Dermit : maria.dermit at qmul.ac.uk 

Jesse Meyer: jesmeyer at mcw.edu
